Revisiting the Truisms of Software Engineering:\\ Does Phase Delay Dramatically Increase Repair Time?

### 2015-03-13 lucas.tex
fixed up various charts and tables. added median phase delay per phase

Summary statistics for the agreement and applicability scores for the RqtsErr and PhaseDelay laws are presented in Figure~\ref{fig:survey_results} \lucas{To add results from other laws}. Responses whose \textbf{applicability} response was ''I don't know'' are ommitted from analysis.

\begin{figure}[!h]
\renewcommand{\baselinestretch}{0.7}
\scriptsize
\begin{center}
\begin{tabular}{c|c|c|c|c|c|c}
Survey & law & N & \multicolumn{2}{c}{agreement} & \multicolumn{2}{c}{applicability} \\ 
 & & mean & median & mean & median \\
\hline 
Practitioners & RqtsErr & 16 & 4.6 & 5 & 4.2 & 4 \\ 
Researchers & RqtsErr & 30 & 3.8 & 4 & 3.8 & 4 \\ 
Researchers & PhaseDelay & 30 & 3.6 & 4 & -- & -- 
\end{tabular} 
\end{center}
\caption{Agreement and applicability of phase delay related axioms.}
\label{fig:survey_results}
\end{figure}

>>>>

Summary statistics for the agreement and applicability scores for the RqtsErr and PhaseDelay laws are presented in Figure~\ref{fig:survey_results}. Responses whose \textbf{applicability} response was ''I don't know'' are ommitted from analysis.

\begin{figure}[!h]
\renewcommand{\baselinestretch}{0.7}
\scriptsize
\begin{center}
\subcaption{Practitioner survey}
\begin{tabular}{l|c|c|c|c|c}
Law & N & \multicolumn{2}{c}{agreement} & \multicolumn{2}{c}{applicability} \\ 
 & & $\bar{x}$ & $\tilde{x}$ & $\bar{x}$ & $\tilde{x}$ \\
\hline 
\textbf{Rqts errors are most expensive...} & 16 & 4.6 & 5 & 4.2 & 4 \\ 
Process maturity improves output & 17 & 4.4 & 4 & 3.9 & 4 \\ 
Most time is spent removing errors & 16 & 4.1 & 4 & 3.9 & 4 \\ 
Missing reqts are hardest to fix & 17 & 4.1 & 4 & 4.0 & 4 \\
Reuse increases prod. and qual. & 16 & 3.9 & 4 & 3.8 & 4 \\
OO-programming reduces errors & 13 & 3.9 & 4 & 3.5 & 4 \\
80-20 rule (defects to modules) & 12 & 3.8 & 4 & 4.0 & 4 \\
Adding manpower to a late project & 15 & 3.7 & 4 & 3.7 & 4 \\
Inspections can remove 90\% of defects & 18 & 3.3 & 4 & 3.5 & 4 \\
Smaller changes have higher error density & 14 & 2.8 & 3 & 3.4 & 3.5 \\
A developer is unsuited to test own code & 17 & 2.6 & 3 & 3.5 & 4
\end{tabular} 
\bigskip
\subcaption{Researcher survey}
\begin{tabular}{l|c|c|c|c|c}
Law & N & \multicolumn{2}{c}{agreement} & \multicolumn{2}{c}{applicability} \\ 
 & & $\bar{x}$ & $\tilde{x}$ & $\bar{x}$ & $\tilde{x}$ \\
\hline 
Process maturity improves output & 4 & 4.0 & 4 & 4.0 & 4 \\
\textbf{Rqts errors are most expensive...} & 30 & 3.8 & 4 & 3.8 & 4   \\ 
80-20 rule (defects to modules) & 6 & 3.7 & 4 & 3.5 & 4 \\
\textbf{PhaseDelay} & 30 & 3.6 & 4 & -- & --  \\ 
Missing reqts are hardest to fix & 7 & 3.6 & 4 & 3.7 & 4 \\
Adding manpower to a late project & 4 & 3.5 & 4 & 3.5 & 4 \\
Inspections can remove 90\% of defects & 7 & 3.4 & 4 & 3.6 & 3 \\
Reuse increases prod. and qual. & 6 & 3.3 & 4 & 3.0 & 4 \\
OO-programming reduces errors & 6 & 3.2 & 4 & 2.7 & 3 \\
Most time is spent removing errors & 6 & 2.8 & 3 & 3.2 & 4 \\ 
Smaller changes have higher error density & 4 & 2.8 & 3 & 4.0 & 4 \\
A developer is unsuited to test own code & 7 & 2.1 & 2 & 2.4 & 3
\end{tabular}

\end{center}
\caption{Agreement and applicability of software engineering axioms.}
\label{fig:survey_results}
\end{figure}

### 2015-03-13 phaseDelay.tex
fixed up various charts and tables. added median phase delay per phase

\usepackage{subfigure}
\usepackage{picture}
\usepackage{wrapfig}
\usepackage{algorithm}
\usepackage{graphicx}
\usepackage{algorithmicx}
\usepackage{algpseudocode}
\renewcommand{\algorithmicrequire}{\textbf{Input:}}
\renewcommand{\algorithmicensure}{\textbf{Output:}} 
\newcommand{\lucas}[1]{\textcolor{red}{LUCAS: #1}} \newcommand{\tim}[1]{\textcolor{orange}{TIM: #1}}
\newcommand{\bill}[1]{\textcolor{blue}{BILL: #1}} 
\newcommand{\carter}[1]{\textcolor{cyan}{CARTER: #1}} 
\newcommand{\sei}[1]{\textcolor{RedViolet}{BILL/FORREST: #1}} 
\newcommand{\todo}[1]{\textcolor{Maroon}{TODO: #1}} 
%\newenvironment{changed}{\par}{\par}

@@

\todo{
\bi
    \item What is the cost-to-fix curve in TSP data? Check against H1 and compare to past literature.
    \item What is the effect of phase delay? Check against H2.
    \item fig12 is great. really important. its from  different decades, right?  so can we add text saying that the general pattern is that the (approx) 15 years between each curve tends to a flattening. not, perhaps, due to process but to better build environs.
    \item but fig12 is blurred in the words. recreate using crisper fonts?
    \item fig 10 text a little blurred. can we re snap that one? or generate it it some higher res form?
    \item figs 13 (fix time rank v phase delay) is hard to read (text)
\ei
}

@@

\begin{figure}[!ht]
 \includegraphics[width=3.3in]{boehm_overlay.png}
 \caption{Cost-to-fix curve from \fig{cost-to-fix} overlayed with TSP data and case study from~\cite{Royce98}.}
 \label{fig:cost-to-fix-tsp}
 \end{figure}

@@

\subsection{Phase delay analysis}
\todo{
\bi
    \item What can we say about \fig{raw}
    \item What is the difference between \fig{raw}
\ei
}

 In the early phases, i.e., Design \& Coding, most of the defects found have a relatively small phase delay. This is ideal considering that the purpose of the early phase reviews is to remove as many defects as possible.

In the TSP data, there is a weak correlation (Kendall's $\tau = 0.19, p < 0.01, 95\% CI$) between a defect's cost-to-fix (minutes of effort) and the defects phase delay (phase removed - phase injected) - see \fig{correlation}.

@@

@@

>>>>

\usepackage{tabularx}
\usepackage{subcaption}
\usepackage{picture}
\usepackage{wrapfig}
\usepackage{algorithm}
\usepackage{graphicx}
\usepackage{algorithmicx}
\usepackage{algpseudocode}
\renewcommand{\algorithmicrequire}{\textbf{Input:}}
\renewcommand{\algorithmicensure}{\textbf{Output:}} 
\newcommand{\lucas}[1]{\textcolor{red}{LUCAS: #1}} \newcommand{\tim}[1]{\textcolor{orange}{TIM: #1}}
\newcommand{\bill}[1]{\textcolor{blue}{BILL: #1}} 
\newcommand{\carter}[1]{\textcolor{cyan}{CARTER: #1}} 
\newcommand{\sei}[1]{\textcolor{RedViolet}{BILL/FORREST: #1}} 
\newcommand{\todo}[1]{\textcolor{Maroon}{TODO: #1}} 
%\newenvironment{changed}{\par}{\par}

@@

\todo{
\bi
    \item What is the cost-to-fix curve in TSP data? Check against H1 and compare to past literature.
    \item What is the effect of phase delay? Check against H2.
    \item \fig{cost-to-fix-tsp} is great. really important. its from  different decades, right?  so can we add text saying that the general pattern is that the (approx) 15 years between each curve tends to a flattening. not, perhaps, due to process but to better build environs.
\ei
}

@@

\begin{figure}[!ht]
 \includegraphics[width=3.3in]{boehm-overlay.pdf}
 \caption{Cost-to-fix curve from \fig{cost-to-fix} overlayed with TSP data and case study from~\cite{Royce98}.}
 \label{fig:cost-to-fix-tsp}
 \end{figure}

@@

\subsection{Phase delay analysis}
\todo{
\bi
    \item What can we say about \fig{raw}
\ei
}

@@

\fig{phase_delay_medians} and \fig{correlation} show that most defects have a relatively small phase delay in our project sample (phase delay is often <= 2). As intended, the Review and Inspection Phases for Requirements, Design, and Code mostly find defects originating in the preceding phase. In contrast, the Testing phases mostly find defects originating in the Code phase.

In \fig{raw}, we present the median fix times of defects based on when they were injected and ultimately removed. Defects injected Before Development follow the most severe scale up as development phases pass, but not on the exponential scale traditionally seen (\fig{cost-to-fix}). Defects injected in Requirements, Design, and Coding phases exhibit virtually no scale-up regardless of the phase in which they are fixed.

%In the TSP data, there is a weak correlation (Kendall's $\tau = 0.19, p < 0.01, 95\% CI$) between a defect's cost-to-fix (minutes of effort) and the defects phase delay (phase removed - phase injected).

@@

\begin{figure}[!ht]
\centering
\begin{tabular}{rrr|l}
    \multicolumn{3}{c|}{Percentiles}\\ 
  25th & 50th & 75th & Phase removed \\ 
  \hline
    2 & 2 & 2 & ReqtsInspect \\ 
    1 & 1 & 1 & ReqtsReview \\ 
    2 & 2 & 2 & HLDInspect \\ 
    1 & 1 & 1 & HLDReview \\ 
    2 & 2 & 2 & DesignInspect \\ 
    1 & 1 & 1 & DesignReview \\ 
    2 & 2 & 2 & CodeInspect \\ 
    1 & 1 & 1 & CodeReview \\ 
    3 & 3 & 6 & UnitTest \\ 
    4 & 4 & 4 & IntTest \\ 
    5 & 5 & 5 & SysTest \\ 
    6 & 6 & 6 & AcceptTest \\ 
  \end{tabular}
\caption{Median phase delay of defects removed per phase} 
\label{fig:phase_delay_medians}
\end{figure}
